---
title: "Student Sit In"
author: "Mirian Maldonado"
date: "10/28/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from the USCDdataframe with multiple variables out of 173 students.



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 

We will use graphical barcharts, numerical tables and infrarential methods to find the p-value. To find out if there is a correlation between where a student sits and their major. 


## Data summary

**Graphical summary**
put the graphic description of the data here

```{r} 
barchartGC(~seat+major, data=UCDdataframe, main='seating+major',type='percent',xlab='seat')
```

The graph shows that Non-Liberal Arts majors prefer the back and middle seats a little more than the front but not by a lot and Liberal Arts majors prefer the front more than the middle and back. But neither likes one seat predominantly more than the other.


**Numerical summary**
put numerical summary here

```{r}
xtab=xtabs(~seat+major,data=UCDdataframe) 
print(xtab)
```

There is not much of a difference between seating preference between majors.

## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(xtab)
```
 
what is the p-value? 0.2173 > 0.05 suggests there is no connection between where one sits and ones major.

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

There is no evidence that certain majors lend to sit in particular areas of the class. The P-value was 0.2173 which is greater than 0.05 so we fail to reject the null hypothesis.

<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->